The dataset used to create the mockup of the dashboards has been handcrafted by the authors.
It consists of different CSV files, each one representing a table. These files describe
the courses within an e-learning platform, the interactions between a user and courses,
the interactions between users, the resources used by the user on the platform, and the user's
results in the courses.

The dataset is composed of the following tables:
\begin{itemize}
    \item 
        \textbf{Completed Course:} This table indicates whether the user has completed something each 
        day or not for the different courses;
    \item 
        \textbf{User Hours Sessions:} This table represents the hours spent by the user on the platform 
        each day and the average hours spent by other users;
    \item 
        \textbf{Resources:} This table represents the hours of use of the different resources that are
        available on the platform for each day;
    \item 
        \textbf{Forum:} This table represents the interactions between users on the forum, showing the number
        of questions asked, the number of answers given, and the number of answers received;
    \item 
        \textbf{Completed Modules Votes:} This table shows the votes obtained by the user for each completed module, 
        categorized by type (theory or exercise).
\end{itemize}

The files produced are tailored on the specific dashboard where used. Some of the previously described files
are duplicated and adapted to the particular needs of the dashboard. For example, the \textbf{Forum} table describes
the interactions for each course or the interactions for each module inside a specific course. The same applies to the
\textbf{Resources} table, where the resources are divided by course or represent the resources used for a particular course.
